---
title: "Assignment 2"
author: "Sai Prasad"
date: "2024-02-20"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

---
title: "Assignment"
author: "Sai Prasad"
date: "2024-02-18"
output:
  pdf_document: default
  html_document: default
  word_document: default
---
#Importing libraries of class, dpylr, caret & Dataset. Created a dataset called as "dataset_universal"
```{r}

library(class)
library(dplyr)
library(caret)
dataset_universal <- read.csv("C:\\Users\\desineni\\OneDrive - Kent State University\\Desktop\\boyapati\\sem_1\\fml\\UniversalBank.csv")

```


Excluding unnecessory columns from the above dataset i.e,, ID, ZIP.Code
```{r}
dataset_universal1 <- dataset_universal[,-1]
dataset_universal1 <- dataset_universal1[,-4]

```

Conveting Personal.Loan into a factor
```{r}
dataset_universal$Personal.Loan=as.factor(dataset_universal$Personal.Loan)
head(dataset_universal$Personal.Loan)
```

Executing above dataset with .na if there is any NA values
```{r}
head(is.na(dataset_universal1))
any(is.na(dataset_universal1))
```
Converting categorical variable into i.e education into dummy variables

Here we are converting Education into factor. There are three levels in Education
```{r}
 
education = as.character(dataset_universal1$Education)

head(dataset_universal1)
dataset_universal2 <- cbind(dataset_universal1[,-6],education)
head(dataset_universal2)

dummymodel<-dummyVars("~education",data = dataset_universal2)
educationdummy<-data.frame(predict(dummymodel,dataset_universal2))
head(educationdummy)
dataset_universal_dummy<-cbind(dataset_universal2[,-12],educationdummy)
head(dataset_universal_dummy)

```
```{r}

set.seed(123)
train<-createDataPartition(dataset_universal_dummy$Personal.Loan,p=0.60,list = FALSE)
train_set<-dataset_universal_dummy[train,]
nrow(train_set)
validation_set<-dataset_universal_dummy[-train,]
nrow(validation_set)
test_set<-data.frame(Age = 40, Experience = 10, Income = 84, Family = 2, CCAvg = 2,  Mortgage = 0, Securities.Account = 0, CD.Account = 0, Online = 1, 
      CreditCard = 1,education1 = 0, education2 = 1, education3 = 0)


summary(train_set)
summary(validation_set)
summary(test_set)
normvar<-c('Age',"Experience","Income","Family","CCAvg","Mortgage","Securities.Account","CD.Account","Online","CreditCard","education1","education2","education3")
normalization_values<-preProcess(train_set[,normvar],method = c('center','scale'))

trainset_norm<-predict(normalization_values,train_set)
summary(trainset_norm)

validationset_norm<-predict(normalization_values,validation_set)
summary(validationset_norm)

testset_norm<-predict(normalization_values,test_set)
summary(testset_norm)
```


#1: Classifying the given customer data
```{r}

set.seed(123)
newgrid<-expand.grid(k=c(1))
newmodel<-train(Personal.Loan~.,data=trainset_norm,method="knn",tuneGrid=newgrid)

newmodel

predicting_test<-predict(newmodel,testset_norm)
predicting_test

```
#Question 2: What is a choice of k that balances between overfiƫng and ignoring the predictor information?
#identifying the best k and finding the best k
```{r}

set.seed(123)
searchGrid <- expand.grid(k=seq(1:20))
model_data<-train(Personal.Loan~.,data=trainset_norm,method="knn",tuneGrid=searchGrid)
model_data

plot(model_data$results$k,model_data$results$Accuracy, type = 'o',pch = 16)


best_k <- model_data$bestTune[[1]]
best_k
```
#Question 3:Confusion matrix for the validation data that results from using the best k
```{r}

library(gmodels)

train_label<-trainset_norm[,7]
validation_label<-validationset_norm[,7]
test_label<-testset_norm[,7]

predicted_validationlabel<-knn(trainset_norm,validationset_norm,cl=train_label,k=5)

CrossTable(x=validation_label,y=predicted_validationlabel,prop.chisq = FALSE)
```
```{r}
#Question 4:Classifying the given customer with best k
set.seed(123)
best_k_grid<-expand.grid(k=c(best_k))
best_k_model<-train(Personal.Loan~.,data=trainset_norm,method="knn",tuneGrid=best_k_grid)
best_k_model

best_k_test<-predict(best_k_model,testset_norm)
best_k_test

```
#Question5:confusion matrix for validation and training sets
#dividing dataset into traning, validation and testing set
```{r}

#Question5:confusion matrix for validation and training sets
#dividing dataset into traning, validation and testing set
set.seed(123)
training_1<-createDataPartition(dataset_universal_dummy$CD.Account ,p=0.50,list = FALSE)
train_set_2<-dataset_universal_dummy[training_1,]
middleset<-dataset_universal_dummy[-training_1,]
nrow(middleset)
training_2<-createDataPartition(middleset$CD.Account,p=0.6,list = FALSE)
validation_set_2<-middleset[training_2,]
test_set_2<-middleset[-training_2,]

nrow(train_set_2)
nrow(validation_set_2)
nrow(test_set_2)

head(train_set_2)
#normalizing trainset_2,validationset_2,testset_2

normvar<-c('Age',"Experience","Income","Family","CCAvg","Mortgage","Securities.Account","CD.Account","Online","CreditCard","education1","education2","education3")
normalization_values_2 <- preProcess(train_set_2[,normvar],method = c('center','scale'))

trainset_norm_2<-predict(normalization_values_2,train_set_2)
summary(trainset_norm_2)

validationset_norm_2<-predict(normalization_values_2,validation_set_2)
summary(validationset_norm_2)

testset_norm_2<-predict(normalization_values_2,test_set_2)
summary(testset_norm_2)

#confusion matrix
library(gmodels)

train_label_2<-trainset_norm_2[,7]
validation_label_2<-validationset_norm_2[,7]
testing_label_2<-testset_norm_2[,7]

predicted_validation_label_2<-knn(trainset_norm_2,validationset_norm_2,cl=train_label_2,k=best_k)

predicted_test_label_2<-knn(trainset_norm_2,testset_norm_2,cl=train_label_2,k=best_k)

confusionmatrix_1<-CrossTable(x=validation_label_2,y=predicted_validation_label_2,prop.chisq = FALSE)
confusionmatrix_2<-CrossTable(x=testing_label_2,y=predicted_test_label_2,prop.chisq = FALSE)


validation_table<-table(validation_label_2,predicted_validation_label_2)
confusionMatrix(validation_table)

test_table<-table(testing_label_2,predicted_test_label_2)
confusionMatrix(test_table)



```
# on comparing the confusion matrix of validation set and testing set it can be seen that accuracy and sensitivity of validation is slightly greater than test set







