---
title: "sboyapa1"
author: "Sai Prasad"
date: "2024-01-26"
output:
  pdf_document: default
  html_document: default
---

 Here uploding my dataset House_rent_Dataset
```{r}
rental_data <- read.csv("C:\\Users\\desineni\\Downloads\\House_Rent_Dataset (1).csv")
```
```{r}
summary(rental_data)
```
 Here printing descriptive statistics for a selection of quantitative from dataset which was "Size"
```{r}
summary(rental_data$Size)
```
 Here printing descriptive statistics for a selection of categorical variable is Area.Locatlity
```{r}
summary(rental_data$Area.Locality)
```
Here I am creating variable "coupon" And assigning it to square root of a rent. Finally applying to new varaible "new_rent" where it means rent after applying the coupon\



```{r}
coupon <- sqrt(rental_data$Rent)
View(rental_data)
View(coupon)
```
```{r}
# Transforming Rent variables of the dataset
new_rent <- (rental_data$Rent-coupon)
head(new_rent)
```
Here I am plotting a scatter plot Size vesus Rent. Because Rent depends on the Size.\ Scale \ x-axis is size of the House \ y-axis is rent of the House
```{r}

plot(rental_data$Size,rental_data$Rent)

```
```{r}
library(ggplot2)
```
```{r}

rental_mean <- aggregate(Rent ~ City, data = rental_data, FUN = mean)

# Creating Barplot Rent Versus City. 
barplot(rental_mean$Rent, names.arg = rental_mean$City)

```
the people living Mumbai have highest Rent whereas the people living Kolkata have  least Rent.\



Source of the data used for this task: https://www.kaggle.com/code/prashantverma13/house-rent-prediction-in-depth-analysis-models/input?select=House_Rent_Dataset.csv

