---
title: "Assignment 4"
author: "Sai Prasad"
date: "2024-03-31"
output:
  pdf_document: default
  html_document: default
---
Here I am importing requrired libraries and dataset. And removing NA (missing) values
```{r}
library(tidyverse)
library(factoextra)
pharma_data<-read.csv("C://Users//desineni//Downloads//Pharmaceuticals (2).csv")
pharma_data<-na.omit(pharma_data)
```
Employing the numerical variables (from 1 to 9) to group the 21 companies into clusters
```{r}
row.names(pharma_data)<-pharma_data[,1]
clustered_data<-pharma_data[,3:11]

```
Here I am scaling the clutertered data
```{r}
set.seed(5097)
scaling_data<-scale(clustered_data)

```

Here I was doing K-means clustering with randomly selected K values.
```{r}
set.seed(5097)
k_mean1<-kmeans(scaling_data,centers = 2, nstart = 15)
k_mean4<-kmeans(scaling_data,centers = 4, nstart = 15)
k_mean8<-kmeans(scaling_data,centers = 8, nstart = 15)

plot_k_mean1<-fviz_cluster(k_mean1,data = scaling_data) + ggtitle("K=2")
plot_k_mean4<-fviz_cluster(k_mean4,data = scaling_data) + ggtitle("K=4")
plot_k_mean8<-fviz_cluster(k_mean8,data = scaling_data) + ggtitle("K=8")

plot_k_mean1
plot_k_mean4
plot_k_mean8


```

Employing WSS (Within-Cluster Sum of Square) and Silhouette scores to identify 
the optimal K value for clustering.

```{r}
K_WSS<-fviz_nbclust(scaling_data,kmeans,method="wss")
K_Silhouette<-fviz_nbclust(scaling_data,kmeans,method="silhouette")
K_WSS
K_Silhouette
dist<-dist(scaling_data,metho='euclidean')
fviz_dist(dist)
```
Based on the WSS, the optimal number of clusters (k) is 2, whereas the Silhouette score suggests k is 5. We are opting for k=5 as it guarantees a lower within-cluster sum of squares while also ensuring satisfactory separation between clusters.



Here I was doing K Means to the required K
```{r}
set.seed(5097)
k_mean5<-kmeans(scaling_data,centers = 5, nstart = 10)
k_mean5
plot_kmeans5<-fviz_cluster(k_mean5,data = scaling_data) + ggtitle("K=5")
plot_kmeans5

clustering_data1<-clustered_data%>%
  mutate(Cluster_no=k_mean5$cluster)%>%
  group_by(Cluster_no)%>%summarise_all('mean')
clustering_data1

```
Below companies are grouped into following clusters:


Cluster_1= BAY,CHTT,IVX


Cluster_2= AVE,ELN,MRX,WPI 


Cluster_3=AGN,PHA


Cluster_4= ABT,AHM,AZN,BMY,LLY,NVS,SGP,WYE


Cluster_5=GSK,JNJ,PFE,MRK




From the clusters formed it can be understood that 


1. Cluster_1 includes companies with extremely poor ROA, ROE, market capitalization, and asset turnover, indicating a high level of risk associated with these firms.


2. Cluster_2  has companies collect firms resembling those in cluster_1, but with a bit less risk involved.


3. Cluster_3 has companies possess an excellent PE_ratio but suffer from very poor ROA and ROE, making them riskier than those in cluster_1.


4. Cluster_4 has collection of businesses with moderate return on equity and return on investment.


5. Cluster_5 has companies exhibiting excellent market capitalization, ROE, and ROA


```{r}
clustering_dataset2<- pharma_data[,12:14] %>% mutate(Clusters=k_mean5$cluster)
ggplot(clustering_dataset2, mapping = aes(factor(Clusters), fill =Median_Recommendation))+geom_bar(position='dodge')+labs(x ='Clusters')
ggplot(clustering_dataset2, mapping = aes(factor(Clusters),fill = Location))+geom_bar(position = 'dodge')+labs(x ='Clusters')
ggplot(clustering_dataset2, mapping = aes(factor(Clusters),fill = Exchange))+geom_bar(position = 'dodge')+labs(x ='Clusters')


```

It's observable that there's a trend between clusters and the Median Recommendation variable. For instance, the first cluster implies a recommendation ranging from hold to moderate buy, while the second cluster leans towards a moderate buy to moderate sell suggestion.
The location graph indicates that a majority of the pharmaceutical companies are based in the US, and there doesn't appear to be a significant pattern beyond that.
The clusters do not exhibit a distinct pattern in relation to the stock exchange, aside from the observation that the bulk of the companies are traded on the NYSE.


Naming clusters:


[Based on the companies listed for each cluster, which seem to represent pharmaceutical firms]


Cluster 1: Innovative Biotech Pioneers.


Cluster 2: Specialty Pharma Developers.


Cluster 3:Focused Healthcare Duo.


Cluster 4: Diversified Healthcare Giants.


Cluster 5: Global Healthcare Leaders.