---
title: "Assignment 5"
author: "Boyapati Sai Prasad"
date: "2023-04-20"
output:
  pdf_document: default
  html_document: default
---

Loading required libraries

```{r}
library(factoextra)
library(dendextend)
library(cluster)
library(tidyverse)
library(knitr)

```
Here i am importing the data
```{r}

cereals_Data<-read.csv("C:\\Users\\CherRyY\\Desktop\\BOYAPATI\\Cereals.csv")
numericData<-data.frame(cereals_Data[,4:16])

```
Here i am removing the missing values

```{r}

miss_ceralas_data<-na.omit(numericData)

```

Standardizing above data
```{r}
normalise_cerals<-scale(miss_ceralas_data)
```

Here i am using Euclidean distance to calculate the distance
```{r}

cerals_distance<-dist(normalise_cerals, method = "euclidian")
```
Hierarchical Clustering is carried out, employing complete linkage
```{r}

hierarchial_CClustering<-hclust(cerals_distance,method = "complete")
plot(hierarchial_CClustering)
```

Rounding the numbers to the nearest decimals
```{r}
round(hierarchial_CClustering$height, 3)
```




Applying AGNES algorithm for CClustering
```{r}
library(dendextend)

HC_Single<-agnes(normalise_cerals, method = "single")
HC_Complete<-agnes(normalise_cerals, method = "complete")
HC_Average<-agnes(normalise_cerals, method = "average")
HC_Ward<-agnes(normalise_cerals, method = "ward")
```

We will now contrast the agglomerative coefficients for average, single, and complete linkage methods.

```{r}

print(HC_Single$ac)
print(HC_Complete$ac)
print(HC_Average$ac)
print(HC_Ward$ac)

```

The ward method exhibits the highest effectiveness with an agglomerative coefficient value of 0.904 among the mentioned approaches. 
Let's proceed to identify the best CClusters.



```{r}

#here i AM using the ward method for hierarchial Clustering
HC_01<-hclust(cerals_distance, method = "ward.D2" )
plot(HC_01,cex=0.6)
rect.hclust(HC_Ward,k=5, border=2:10)
```

From the conclusions drawn from the ward method graphs, it is evident that the optimal k value is 5.
Therefore, we will choose five CClusters. Next, let's utilize the ward approach
to map AGNES


```{r}
sub_grouping <- cutree(HC_01,k=5)
table(sub_grouping)
cereals_groupings <- as.data.frame(cbind(normalise_cerals,sub_grouping))
```

Let's represent the results on a scatter plot.
```{r}
fviz_cluster(list(data = normalise_cerals, cluster = sub_grouping))
```

Let's identify the top Cluster of breakfast cereals that are low in sugar and sodium, high in protein, and high in fiber.

Choosing the Cluster of nutritious cereals.

```{r}
New_Cereals <- numericData
Ncereal_omit <- na.omit(New_Cereals)
CCluster <- cbind(Ncereal_omit, sub_grouping)
CCluster[CCluster$sub_grouping==1,]
```

```{r}
CCluster[CCluster$sub_grouping==2,]
```


```{r}
CCluster[CCluster$sub_grouping==3,]
```


```{r}
CCluster[CCluster$sub_grouping==4,]
```


```{r}
CCluster[CCluster$sub_grouping==5,]
```
Let's calculate the average rating to determine the healthiest cluster of grain cereals.
```{r}
mean(CCluster[CCluster$sub_grouping==1,"rating"])
mean(CCluster[CCluster$sub_grouping==2,"rating"])
mean(CCluster[CCluster$sub_grouping==3,"rating"])
mean(CCluster[CCluster$sub_grouping==4,"rating"])
mean(CCluster[CCluster$sub_grouping==5,"rating"])

```

Subgroup 1 has the highest mean rating of 73.84446, as indicated by the statistics above. Therefore, the healthy diet CCluster should be selected from subgroup 1.








 